---
title: "filter_join"
author: "Katie"
date: "09/03/2022"
output: html_document
---

library(tidyverse)
library(readxl)
library(here) 
library(kableExtra)


# Read in data: 

fish <- read_csv(here("data", "fish.csv"))

kelp_abur <- read_excel(here("data", "kelp.xlsx"), sheet = "abur")

#filter data

fish_garibaldi <- fish %>% 
  filter(common_name == "garibaldi")

fish_mohk <- fish %>% 
  filter(site == "mohk")

fish_over50 <- fish %>% 
  filter(total_count >= 50)

fish_3sp <- fish %>% 
  filter(common_name == "garibaldi" | 
           common_name == "blacksmith" | 
           common_name == "black surfperch")

fish_3sp <- fish %>% 
  filter(common_name %in% c("garibaldi", "blacksmith", "black surfperch"))

fish_2sp <- fish %>% 
  filter(common_name %in% c("rock wrasse", "senorita"))
  
fish_gar_2016 <- fish %>% 
  filter(year == 2016 | common_name == "garibaldi")

aque_2018 <- fish %>% 
  filter(year == 2018, site == "aque")
  
abur_2018 <- fish %>% 
  filter(year == 2018 & site == "abur")

 low_gb_wr <- fish %>% 
  filter(common_name %in% c("garibaldi", "rock wrasse"), 
         total_count <= 10) 

 fish_bl <- fish %>% 
  filter(str_detect(common_name, pattern = "black")) 

fish_it <- fish %>% 
  filter(str_detect(common_name, pattern = "it"))

#join data in different tables

abur_kelp_fish <- kelp_abur %>% 
  full_join(fish, by = c("year", "site")) 
kelp_fish_left <- kelp_abur %>% 
  left_join(fish, by = c("year","site"))
kelp_fish_injoin <- kelp_abur %>% 
  inner_join(fish, by = c("year", "site"))

#filtering & joining
my_fish_join <- fish %>% 
  filter(year == 2017, site == "abur") %>% 
  left_join(kelp_abur, by = c("year", "site")) %>% 
  mutate(fish_per_frond = total_count / total_fronds)
```{r}
knitr::kable(my_fish_join)
```
```{r} my_fish_join %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", 
                full_width = FALSE)
```

library(tidyverse)
library(here)  
library(janitor) 
install.packages("paletteer")
library(paletteer) 

us_landings <- read_csv(here("data","noaa_landings.csv"),
                        na = "no data")

summary(us_landings)
View(us_landings)
names(us_landings)
head(us_landings)
tail(us_landings)
salmon_clean <- us_landings %>% 
  clean_names() %>% # Make column headers snake_case
  mutate(
    afs_name = str_to_lower(afs_name)
  ) %>% # Converts character columns to lowercase
  mutate(dollars_num = parse_number(dollars_usd)) %>% # Just keep numbers from $ column
  filter(str_detect(afs_name, pattern = "salmon")) %>% # Only keep entries w/"salmon"
  separate(afs_name, into = c("group", "subgroup"), sep = ", ") %>% # Note comma-space
  drop_na(dollars_num) # Drop (listwise deletion) any observations with NA for dollars_num


```{r}
salmon_us_annual <- salmon_clean %>% 
  group_by(year, subgroup) %>% 
  summarize(
    tot_value = sum(dollars_num, na.rm = TRUE),)
```
#plot of salmon by year by sub-group

```{r}
salmon_gg <- 
  ggplot(salmon_us_annual, 
         aes(x = year, y = tot_value, group = subgroup)) +
  geom_line(aes(color = subgroup)) +
  theme_bw() +
  labs(x = "year", y = "US commercial salmon value (USD)")
```
salmon_gg <- 
  ggplot(salmon_us_annual, 
         aes(x = year, y = tot_value, group = subgroup)) +
  geom_line(aes(color = subgroup)) +
  theme_bw() +
  labs(x = "year", y = "US commercial salmon value (USD)")

salmon_us_annual <- salmon_clean %>% 
  group_by(year, subgroup) %>% 
  summarize(
    tot_value = sum(dollars_num, na.rm = TRUE),
  )
  
salmonplot <- 
  ggplot(salmon_us_annual, 
         aes(x = year, y = tot_value, group = subgroup)) +
  geom_line(aes(color = subgroup)) +
  theme_bw() +
  labs(x = "year", y = "US commercial salmon value (USD)")

ggplot(salmon_us_annual, 
         aes(x = year, y = tot_value, group = subgroup)) +
  geom_line(aes(color = subgroup)) +
  theme_bw() +
  labs(x = "year", y = "US commercial salmon value (USD)")
  
View(palettes_d_names)
 ggplot(salmon_us_annual, 
         aes(x = year, y = tot_value, group = subgroup)) +
  geom_line(aes(color = subgroup)) +
  theme_bw() +
  labs(x = "year", y = "US commercial salmon value (USD)") +
  scale_color_paletteer_d("RSkittleBrewer::smarties")


