---
title: "filter_join"
author: "Katie"
date: "09/03/2022"
output: html_document
---

library(tidyverse)
library(readxl)
library(here) 
library(kableExtra)


# Read in data: 

fish <- read_csv(here("data", "fish.csv"))

kelp_abur <- read_excel(here("data", "kelp.xlsx"), sheet = "abur")

#filter data

fish_garibaldi <- fish %>% 
  filter(common_name == "garibaldi")

fish_mohk <- fish %>% 
  filter(site == "mohk")

fish_over50 <- fish %>% 
  filter(total_count >= 50)

fish_3sp <- fish %>% 
  filter(common_name == "garibaldi" | 
           common_name == "blacksmith" | 
           common_name == "black surfperch")

fish_3sp <- fish %>% 
  filter(common_name %in% c("garibaldi", "blacksmith", "black surfperch"))

fish_2sp <- fish %>% 
  filter(common_name %in% c("rock wrasse", "senorita"))
  
fish_gar_2016 <- fish %>% 
  filter(year == 2016 | common_name == "garibaldi")

aque_2018 <- fish %>% 
  filter(year == 2018, site == "aque")
  
abur_2018 <- fish %>% 
  filter(year == 2018 & site == "abur")

 low_gb_wr <- fish %>% 
  filter(common_name %in% c("garibaldi", "rock wrasse"), 
         total_count <= 10) 

 fish_bl <- fish %>% 
  filter(str_detect(common_name, pattern = "black")) 

fish_it <- fish %>% 
  filter(str_detect(common_name, pattern = "it"))

#join data in different tables

abur_kelp_fish <- kelp_abur %>% 
  full_join(fish, by = c("year", "site")) 
kelp_fish_left <- kelp_abur %>% 
  left_join(fish, by = c("year","site"))
kelp_fish_injoin <- kelp_abur %>% 
  inner_join(fish, by = c("year", "site"))

#filtering & joining
my_fish_join <- fish %>% 
  filter(year == 2017, site == "abur") %>% 
  left_join(kelp_abur, by = c("year", "site")) %>% 
  mutate(fish_per_frond = total_count / total_fronds)
```{r}
knitr::kable(my_fish_join)
```
```{r} my_fish_join %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", 
                full_width = FALSE)
```


